---
title: "PA1_template"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### reading file

```{r}
df <- read.csv('activity.csv')
```



### What is mean total number of steps taken per day?
For this part of the assignment, you can ignore the missing values in the dataset.


```{r, message=FALSE}
library(dplyr)
a<- df %>% group_by(date) %>% summarise(total_steps = sum(steps, na.rm = TRUE))
hist(a$total_steps)
```
```{r}
summarise(a,mean = mean(a$total_steps,na.rm = TRUE), med =median(a$total_steps,na.rm = TRUE))
```
### What is the average daily activity pattern?

```{r}
b<- df %>% group_by(interval) %>% summarise(mean_steps = mean(steps, na.rm = TRUE))
b %>% plot( type = "l")
b$interval[which.max(b$mean_steps)]
```
### Imputing missing values
Note that there are a number of days/intervals where there are missing values (coded as \color{red}{\verb|NA|}NA). The presence of missing days may introduce bias into some calculations or summaries of the data

```{r}
sum(is.na(df))
```

```{r}
#strategy: filling everything with 1
df2 <- df 
df2[is.na(df2)] <- 1
c<- df2 %>% group_by(date) %>% summarise(total_steps = sum(steps))
hist(c$total_steps)
c %>% summarise(mean = mean(total_steps), med =median(total_steps))
```
### Are there differences in activity patterns between weekdays and weekends?

```{r}
library(ggplot2)
df2$weekday <- ifelse(weekdays(as.Date(df2$date)) %in% c('Sunday','Saturday'),'Weekend','Weekday')
d<- df2 %>% group_by(interval,weekday) %>% summarise(avg_steps = mean(steps))
d %>% ggplot(aes(interval,avg_steps)) +geom_line() +facet_wrap(~weekday)
```

